Eye in a Disk: eyeIntegration human pan-eye and body transcriptome database version 1.00

### 2019-03-01 manuscript.Rmd
updating last section

While organoid and retina tissues are highly similar at a pan-transcriptome level, differential expression analysis between organoid and fetal retina reveals differences in related groups of genes. We  Analysis of broad trends in GO term enrichment between differentially expressed genes shows that the HOXB family and protocadherins are differentially expressed between fetal retina and organoids. We noticed that several BRN3/POU4F genes were also differentially regulated

>>>>

To identify specific changes between organoid and retina tissue, we did differential gene expression and GO term enrichment analyses. GO term enrichment identified cell adhesion (protocadherins) and patterning (HOXB family) as enriched gene sets. We also noticed that several RGC markers appeared to have lower expression in the organoids compared to the fetal tissue `r paste0(fig_cap(name = 'tsneFetalRetina', display = 'cite'),'B')`.

We plotted these sets of genes 
Analysis of broad trends in GO term enrichment between differentially expressed genes shows that the HOXB family and protocadherins are differentially expressed between fetal retina and organoids. We noticed that several BRN3/POU4F genes were also differentially regulated
